Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-15 paper/manuscript.Rmd
Q5

5) In relation to all the previous questions: how do individuals vary in their
propensity to swim and their assessment of the costs and benefits of swimming
between islands? We observed some individuals that regularly engaged in swimming
events, while others were never observed swimming in the ocean? Our existing research on individual behavioural variation in caribou movement ecology The forage
limitation hypothesis is thought to apply uniformly across populations, but
individual caribou could evaluate the costs and benefits of swimming
differently. It is possible that some individuals, in our case ~10%, considered
swimming to be less costly or perceived competition or predation more acutely
than their conspecifics.

>>>>

5) In relation to all the previous questions: how do individuals vary in their
propensity to swim and their assessment of the costs and benefits of swimming
between islands? We observed some individuals that regularly engaged in swimming
events, while others were never observed swimming in the ocean? Our existing
research on individual behavioural variation in caribou movement ecology
]@Webber2020] provides a basis to investigate the role of inherent individual
differences in swimming behaviour. Specifically, the forage limitation
hypothesis applies uniformly across populations, but individuals could evaluate
the costs and benefits of swimming differently.
